---
title: "ADA Midterm Code"
output: html_document
date: "2022-10-14"
---
#Question 3: Using the titanic dataset located at "https://github.com/kijohnson/Data", prepare an R markdown file that shows the code for a) importing the dataset, b) determining the median age for by passenger class, and c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. Report the medians by passenger class and upload a PDF or picture of your plot.
```{r}
#0: Install packages and open libraries:
pacman::p_load(tidyverse)

#a: importing dataset:
midterm_titanic <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")

#b: determining the median age by passenger class:
midterm_titanic %>%
    group_by(Pclass) %>%
    summarize(median_age = median(Age))

#c: creating plot of median age by passenger class:
class(midterm_titanic$Pclass) #determining class of "Pclass" = "numeric"
class(midterm_titanic$Age) #determining class of "Age" = "numeric"

plot1 <- ggplot(midterm_titanic, aes(x=as_factor(Pclass), y=Age)) + 
  geom_boxplot()+
  labs(title = "Age by Passenger Class", y="Age", x="Passenger Class") #creating box plot of variables with  "Pclass" coded as factor

plot1 #displaying plot
```

#Question 4b: Next, add code to determine the percentage of males and females by class. Save this new version and push the new version to your Github repository

```{r}
#4b: determining % of sex by class:
midterm_titanic %>%
    group_by(Sex, Pclass) %>%
    summarize(percent = 100 * n() / nrow(midterm_titanic))
```














